dispRity demo for ecological data

### 2015-10-07 doc/dispRity-ecology-demo.Rnw
Updated ecological example

Note that we use the \texttt{release} branch here which is version \Sexpr{packageVersion("dispRity")}.
If you want the piping-hot (and full of bugs) version, change the option \texttt{ref = "release"} to \texttt{ref = "master"}.
This package depends mainly on the \texttt{ape} package and the \texttt{timeSliceTree::paleotree} function.

@@

<<PCAplot, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
## The x and y axis represent the two first dimensions of the PCA
x <- ord_matrix[, 1]
y <- ord_matrix[, 2]
## The colors will represent the treatments
cols <- sub("treat1", "red", treatments)
cols <- sub("treat2", "blue", cols)
## The symbols will represent the depth
pchs <- sub(1, 16, depth)
pchs <- as.numeric(sub(2, 17, pchs))
## Graphical option
par(bty = "n")
## A classic PCA plot
plot(x, y, col = cols, pch = pchs, xlab = "PCA1", ylab = "PCA2",
    xlim = range(x) + c(0, 100))
@

@@

In practice, the \dispRity function intakes a pair of class and summary metrics as a definition of disparity.
Several of these metrics are implemented in other packages (like \texttt{stats::median}, \texttt{base::sum}, etc.) and this package proposes several metrics listed in \texttt{dispRity.metric} (see \texttt{?dispRity.metric}).
It is even possible to use your very own class and summary metrics!
This will be actually heavily encouraged and facilitate with the \texttt{make.metric} function in a future version.

>>>>

Note that we use the \texttt{master} branch here which is version \Sexpr{packageVersion("dispRity")}.
This is the piping-hot latest version.
If you want a more stable (and tested version), change \texttt{ref = "master"} to \texttt{ref = "release"}.
This package depends mainly on the \texttt{ape} package and the \texttt{timeSliceTree::paleotree} function.

@@

<<PCAplot, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
## The x and y axis represent the two first dimensions of the PCA
x <- ord_matrix[, 1]
y <- ord_matrix[, 2]
## The colors will represent the treatments
cols <- sub("a", "red", treatments)
cols <- sub("b", "blue", cols)
## The symbols will represent the depth
pchs <- sub(1, 16, depth)
pchs <- as.numeric(sub(2, 17, pchs))
## Graphical option
par(bty = "n")
## A classic PCA plot
plot(x, y, col = cols, pch = pchs, xlab = "PCA1", ylab = "PCA2",
    xlim = range(x) + c(0, 100))
@

@@

In practice, the \dispRity function intakes a pair of class and summary metrics as a definition of disparity.
Several of these metrics are implemented in other packages (like \texttt{stats::median}, \texttt{base::sum}, etc.) and this package proposes several metrics listed in \texttt{dispRity.metric} (see \texttt{?dispRity.metric}).
But it is even possible to use your very own class and summary metrics! Or even any metric you decide makes sense (note that this is not yet implemented in v.\Sexpr{packageVersion("dispRity")}).
This will be actually heavily encouraged and facilitate with the \texttt{make.metric} function in a future version.
